%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}

\usepackage{xcolor}
\usepackage[colorlinks = true, linkcolor = black, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\myHref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Albert Suarez} & Email : hi@asuarez.dev\\
  \myHref{https://asuarez.dev}{https://asuarez.dev} & Mobile : (+34) 644 577 607 \\
  Github : \myHref{https://github.com/AlbertSuarez}{@AlbertSuarez} & Linkedin : \myHref{https://www.linkedin.com/in/albertsuarezmolgo/}{/in/albertsuarezmolgo} \\
\end{tabular*}

%-----------ABOUT ME------------------
\section{About me}
I'm a Software Engineer graduated at Universitat Politecnica de Catalunya, BarcelonaTech. I am hard worker, friendly, positive and active. Moreover, polite and I have excellent personal skills. Capacity for teamwork and lifelong learning. Always ready to help other members of the team.

%-----------EDUCATION-----------------
\section{Education \& Training}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitat Politecnica de Catalunya}{Barcelona, Spain}
      {Bachelor degree in Software Engineering;  GPA: 7.32/10}{Sep. 2013 -- Jun. 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Working Experience}
  \resumeSubHeadingListStart

\resumeSubheading
      {Restb.ai}{Barcelona, Spain}
      {Principal Software Engineer}{Jun 2018 - Present}
      \resumeItemListStart
        \resumeItem{Description}
          {Working in this hot start-up in Barcelona, my duties are managing all the stack from the backend to the frontend along with managing and leading a team of young engineers, mentoring and helping them to reach the goals of Restb.ai. Python is the most used language, but Lua, JavaScript, and TypeScript as well. Some other stuff like Docker, Nginx, Machine Learning frameworks, Kubernetes, AWS, Flask, OpenAPI, Celery, Angular and more are being used every day in this role.}
      \resumeItemListEnd

    \resumeSubheading
      {HackUPC}{Barcelona, Spain}
      {Co Director \& Organiser}{Jun 2016 - May 2019}
      \resumeItemListStart
        \resumeItem{Description}
          {Co-directed the fourth edition of UPC student hackathon. Attending 700 hackers from around the world. Responsible for managing and coordinating a team of 25 organizers, event design, logistics, volunteers, sponsorship and marketing. Also working as a director of the Sponsorship and Staff departments in other editions of the anual event.}
      \resumeItemListEnd

    \resumeSubheading
      {UPCnet}{Barcelona, Spain}
      {Software Engineer Intern}{Sep 2016 - Jul 2017}
      \resumeItemListStart
        \resumeItem{Description}
          {I was part of a big information technology consulting firm. In order to carry out my duties, I had to use programming languages like Java, frameworks such as Spring or Hibernate, working with WebServices (SOAP, WSDL...), IDEAs like Spring Tool Suite or IntelliJ, and designing websites with HTML, CSS, JavaScript, Bootstrap, Sass, Less, JQuery and Handlebars.}
      \resumeItemListEnd

    \resumeSubheading
      {ASES Academy}{Barcelona, Spain}
      {Teacher}{Feb 2016 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Description}
          {Teacher of two subjects for university students: Data Structures and Algorithms and Operative Systems. I taught groups of students between 20 to 30 people.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{ObjectCut}
      {Website that takes a picture and a set of object names and crops the objects that you specified automagically using PyTorch.}
    \resumeSubItem{SearchLy}
      {Similarity search API based on the meaning of song lyrics using word2vec.}
    \resumeSubItem{Donework}
      {A content generator given a table of contents using Deep Learning and a Search similarity engine.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming}{: Python, JavaScript, Java, C++}
      \textbf{Experience with}{: Software \& API Design, Docker, Flask, Nginx, OpenAPI, Ruby, Lua, ML Frameworks, Android, SQL, Web development, Git, Scrum.}
    }
    \item{
      \textbf{Native}{: Spanish, Catalan}
      \textbf{Advanced}{: English (General IELTS 6)}
      \textbf{Basic}{: French}
    }
    \item{
      \textbf{Hobbies}{: Photography, Soccer, Travel, Music, Guitar, Swim}
    }
    \item{
      \textbf{Hackathon participation}{: Attended to 21 hackathons (15 different) in 7 distinct countries. 15 as a participant, 5 as an organizer and 1 as a sponsor.}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
